\documentclass[10pt]{article} %Sets the default text size to 11pt and class to article.

\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
%Sets the geometry for the page
\geometry{letterpaper,portrait,margin=0.5in}

%Reduces space between section declarations
\titlespacing*{\section}{0pt}{0ex}{0ex}

%Deletes the page number at the bottom of the page
\pagenumbering{gobble}


\begin{document}

%Block for personal information
\LARGE\noindent\rightline{Steven Sheffey}
\normalsize
\noindent\rightline{5591 Hunters Point Pike}
\noindent\rightline{Lebanon, TN 37087}
\noindent\rightline{615-879-6670}
\noindent\rightline{stevensheffey4@gmail.com}
\noindent\rightline{\href{https://github.com/Starfys}{Github:Starfys}}

%Horizontal rule
\hrulefill

%Main table for content
%Syntax for a line is
%Section label & content \\
\renewcommand\arraystretch{0.1}
\begin{tabularx}{\textwidth}{p{3cm} X}
\section*{Experience}

& \section*{System Administrator (Aug 2014 - present)}
Middle Tennessee State University - Computer Science Department
\begin{itemize}
\setlength{\itemsep}{1pt}
\item Maintained and created production Debian servers to satisfy a variety of departmental needs.
\item Performed various basic maintenance tasks for multiple computer labs
\item Designed an automated and flexible storage monitoring solution.
\item Created a scheduling and appointment system
\item Improved security of several existing production servers
\end{itemize}
\section*{MTSU Makers Club President (Aug 2015 - Present)}
Middle Tennessee State University - MTSU Makers
\begin{itemize}
\setlength{\itemsep}{1pt}
\item Created a makers space in cooperation with the MTSU library to provide resources for students interested in software and hardware development
\item Gave a lecture and demonstration of ethical hacking in order to promote awareness of modern issues in network security.
\item Designed a robust temperature monitoring system to evaluate the efficiency of on-campus heating and cooling systems.
\end{itemize}\\ 
\section*{Education} & \section*{Middle Tennessee State University}
B.S. Computer Science (Aug 2014 - Present)\\
\section*{Projects} &
\section*{Professional}
\begin{description}[noitemsep]
    \item[Sustainability Project] A distributed, robust, and efficient temperature monitoring system using Raspberry Pi and Python. Uses a minimal GNU/Linux operating system to maximize performance.
    \item[Makers Infrasructure] An LDAP/NFS-based server used to provide centralized access to development resources for club members
    \item[Appointment System] A calendar system written in PHP used to schedule access to a departmental meeting room
\end{description}
\section*{Personal}
\begin{description}
    \setlength{\itemsep}{1pt}
    \item [ss-neural-net] A simple neural net implementation in c++
    \item [octo-computing-machine] A testing ground for A.I in an agar.io-like environment
\end{description}\\
\section*{Proficiencies} &
\begin{description}
    \setlength{\itemsep}{1pt}
    \item[Linux:] Knowledge of most of the structure of the Linux operating system. Professional experience with Debian.
    \item[C++] Primarily used for any performance-dependent project. Most coursework and programming challenges done with C++.
    \item[Python] Used extensively for any sort of api access or automation scripting.
\end{description}\\

\section*{Awards} & 
\begin{description}
    \item[2015 Outstanding Sophomore Award] Awarded by the MTSU Computer Science Department to the most impressive sophomore in the department
    \item[ACM ICPC] 6th place in 2015 regional ACM International Collegiate Programming Contest
\end{description}


\end{tabularx}
\end{document}
